Understanding the Lomb-Scargle Periodogram

### 2017-09-13 PracticalLombScargle.tex

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig21_kepler_multiterm}
  \caption{Multi-term models (left) and their corresponding periodograms (right)
    for the kepler data shown in \fig{kepler-data}
    \figlabel{kepler-multiterm}}
\end{figure}

@@

\fig{failure-modes} demonstrates this for some simulated data.
The data consist of 60 noisy observations each of 1,000 simulated light
curves within a span of 180 days.
The window is typical of ground-based data, with each observation recorded
within a few hours before or after midnight each night.
The left panel shows the results: the peridogram peak coincides with the true
period in under 50\% of cases, and the modes of failure lead to noticeable
patterns in the resulting plot.
Though these are simulated observations, the pattern seen here is typical of
real observations: see, for example, \citet{VanderPlas2015}
and \citet{Long2016} which show similar plots for RR Lyrae candidates from
the Sloan Digital Sky Survey.

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig21_kepler_multiterm}
  \caption{Multi-term models (left) and their corresponding periodograms (right)
    for the Kepler data shown in \fig{kepler-data}
    \figlabel{kepler-multiterm}}
\end{figure}

@@

\fig{failure-modes} demonstrates this for some simulated data.
The data consist of 60 noisy observations each of 1,000 simulated light
curves within a span of 180 days.
The window is typical of ground-based data, with each observation recorded
within a few hours before or after midnight each night.
The left panel shows the results: the periodogram peak coincides with the true
period in under 50\% of cases, and the modes of failure lead to noticeable
patterns in the resulting plot.
Though these are simulated observations, the pattern seen here is typical of
real observations: see, for example, \citet{VanderPlas2015}
and \citet{Long2016} which show similar plots for RR Lyrae candidates from
the Sloan Digital Sky Survey.
